\tool: Automated Generation of Diversified Tests from Existing Maps \alessio{Title is not final}

### 2021-07-16 paper/main.tex
Included new data from maps

We demonstrated \tool in the context of the 2021 IEEE Test AI Challenge
by testing state-of-art self-driving car software using an industrial driving simulator. In a matter of minutes, \tool identified many relevant tests from five maps of different sizes and complexity (up to $170$ junctions) and selected $20\%$ of those test cases for execution in the best case. 
%
The evaluation results showed that tests cases generated by \tool resulted in quantifiably different trajectories of the test subject and exposed issues in the test subject and its integration with the simulation platform.
\alessio{Update numbers with missing maps}
\end{abstract}

% CubeTown
%1. 10 paths
%2. distance 1.9: 8 paths
%3. 10 cells: 5 paths
%4. 12 intersections
%BorregasAve
%1. 28 paths
%2. distance 1.9: 20 paths
%3. 10 cells: 16 paths
%4. 29 intersections
%Shalun
%1. 140 paths
%2. distance 1.9: 110 paths
%3. 10 cells: 33 paths
%4. 169 intersections

>>>>

We demonstrated \tool in the context of the 2021 IEEE Test AI Challenge
by testing state-of-art self-driving car software using an industrial driving simulator.
In a matter of minutes, \tool analyzed five maps of different complexity (from $2$ to more than $15$ junctions),
identified more than $1100$ relevant driving scenarios in them, and selected on average half of
them for the execution.
%
The evaluation results showed that tests cases generated by \tool from the selected driving scenarios
resulted in quantifiably different trajectories of the test subject and exposed issues in it.

\end{abstract}

%CubeTown
%1. 10 paths
%2. distance 1.9: 8 paths
%3. 10 cells: 5 paths
%4. 2 intersections
%BorregasAve
%1. 28 paths
%2. distance 1.9: 20 paths
%3. 10 cells: 16 paths
%4. 2 intersections
%Shalun
%1. 140 paths
%2. distance 1.9: 110 paths
%3. 10 cells: 33 paths
%4. 14 intersections
%SanFrancisco
%1. 806 paths
%2. distance 1.9: 535 paths
%3. 10 cells: 52 paths
%4. 89 intersections
%Gomentum
%1. 126 paths
%2. distance 1.9: 110 paths
%3. 10 cells: 25 paths
%4. 25 intersections
